---
title: "Data Analysis: Predict the age of a house built before 1940 based on the number of rooms and tax rate"
output: html_notebook
---
```{r}

```

Using 2 libraries: tidyverse & ggplot2
The Boston data is in the MASS package
My project using variables: rm (number of rooms), age (how old the house is), tax, chas (location of housing nearby Charles river or not - variable to increse the accuracy of model)
-> Create a new dataframe contains only 4 variables and check whether we have any NA cell in new df
```{r}
library(tidyverse)
library(ggplot2)
library(MASS)
Boston
dim(Boston)
df <- Boston[,c('chas','rm','age','tax')]
df
```
Overview of the new dataframe:
+ str(): display a structure of an R object
+ summary(): display the min, max, median, mean of each variable
+ cor(): compute the correlation coefficienct 
```{r}
str(df)
summary(df)
head(df)
```
Correlation Test: cor()
-> Meaning: 
+ The average number of rooms has a negative coefficient with age (dependent variable) 
+ While the tax rate has a positive coefficient with age (dependent variable) 
```{r}
pairs(df[,c(1:4)])
cor(df)
```

Assign plot (histogram and boxplot) for each variable
```{r}
#Age variable
ggplot(df,aes(x=age)) + geom_histogram(bins = 30, aes(y=..density..))+theme_classic() + geom_density()
ggplot(df, aes(x=age)) + geom_boxplot() + theme_classic() 
#rm variable
ggplot(df,aes(x=rm)) + geom_histogram(bins = 30, aes(y=..density..))+theme_classic() + geom_density()
ggplot(df, aes(x=rm)) + geom_boxplot() + theme_classic() 
#tax variable
ggplot(df,aes(x=tax)) + geom_histogram(bins = 30, aes(y=..density..))+theme_classic() + geom_density()
ggplot(df, aes(x=tax)) + geom_boxplot() + theme_classic() 
```
Scatter diagram to show the relationship between dependent var (age) and each independent var (rm & tax)

```{r}
#age & rm
ggplot(df, aes(rm,age)) + geom_point() + geom_smooth(formula = y~x, method = loess)
#age & tax
ggplot(df, aes(tax,age)) + geom_point() + geom_smooth(formula = y~x, method = loess)
```
3 linear regression models: 2 single linear regression models & one multi-variables regression model
+ Model 1: age and rm: Heteroscedasticity -> not a good linear regression model
+ Model 3: age, rm and tax
```{r}
(model1 <- lm(age~rm, data =df))
summary(model1)
par(mfrow = c(2,2))
plot(model1)
shapiro.test(model1$residuals)
```
+ Model 2: age and tax
```{r}
(model2 <- lm(age~tax, data =df))
summary(model2)
par(mfrow = c(2,2))
plot(model2)
shapiro.test(model2$residuals)
```
+ Model 3: age, rm and tax
```{r}
(model3 <- lm(age~tax+rm, data =df))
summary(model3)
par(mfrow = c(2,2))
plot(model3)
shapiro.test(model3$residuals)
```
Improve the accuracy of model using dummy variable CHAS
+ Create one data-frame with CHAS == 1: 35 rows x 4 cols
+ Model 3_1: multi-variables (age,tax,rm) linear regression with dataframe where chas==1
```{r}
(df2 <- filter(df, chas ==1))
summary(df2)
(model3_1 <- lm(age~ df2$tax + df2$rm, data =df2))
summary(model3_1)
```
Improve the accuracy of model using dummy variable CHAS
+ Create one data-frame with CHAS == 0: 471 rows x 4 cols
+ Model 3_1: multi-variables (age,tax,rm) linear regression with dataframe where chas==1
```{r}
(df3 <- filter(df, chas ==0))
summary(df3)
(model3_2 <- lm(age~ df3$tax + df3$rm, data =df3))
summary(model3_2)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Cmd+Option+I*.
When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Cmd+Shift+K* to preview the HTML file). 
The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.

